Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-14 RET_Hosts.tex
Adding to metallicity discussion

The sample of DES RETs shows a preference for low metallicity host environments. The PDF displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs. There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies. The aversion of high-metallicity systems is not as strong as for SLSNe. On first viewing, this is suggestive of a stripped-envelope, massive-star origin for RETs. There are however several selection biases that need to be considered.

>>>>

The sample of DES RETs shows a preference for low metallicity host environments. The PDF displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs. There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies. The aversion of high-metallicity systems is not as strong as for SLSNe. On first viewing, this is suggestive of a stripped-envelope, massive-star origin for RETs. There are however several selection biases that need to be considered. Firstly, metallicity PDF is derived from a subset of the total sample of RETs. under half (49/106) have secure host galaxy redshifts, of which it was possible to derive a metallicity for 37 host galaxies. If the galaxies without redshifts and metallicities are systematically higher in metallicity than those for which measurements were possible,
